\documentclass[sigconf]{acmart}
%\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\pagestyle{plain} % removes running headers

\usepackage{booktabs} % For formal tables
\usepackage{listings}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

\begin{document}
\title{Analyzing Python Package Dependency}

\author{Avadhoot Agasti}
\email{aagasti@indiana.edu}

\author{Abhishek Gupta}
\email{abhigupt@iu.edu}

\begin{abstract}

The Python packages have complex nature of inter-dependencies. Creating
network structure of the package dependency can help in understanding several
 aspects of these dependencies. For example, we can easily understand the
 most basic packages and the packages which have complex dependencies. We can
  also understand the nature of this network (scalefree, random graph etc)
  and then utilize the concepts from these network structure.  Further,
this analysis can be extended to any other programming language to understand
the package network. The scope of this project is to focus on python based
packages and navigate to all dependent packages to build a network graph of
these packages and then analyze this network.
\end{abstract}

\keywords{scale-free, random networks, small-world, packages}

\maketitle

\input{introduction}
\input{motivation}
\input{requirements}
\input{technicalsolution}
\input{graphanalysis}
\input{relatedwork}

%\input{similartechnologies}

%\input{conclusion}

%\end{document}  % This is where a 'short' article might terminate


\section{Acknowledgements}
 The authors thank Prof. YY Ahn for his technical guidance. The
 authors would also like to thank TAs of Network Science class for their valued
 support. 

\section{Repo} 
 All project and report document can be found at \href{https://github.com/avadhoot-agasti/netsci-project/blob/master/report/main.pdf}{github project}.

\nocite{*}
\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
